---
title: "cCRE_size"
format: html
editor: visual
---

R Quarto file to visualize size (bp) distribution of TFBS clusters or candidate CREs as well as final size confirmation and descriptive statistics
on the high confidence CREs (hCREs)
## cCRE (162) Size distribution

```{r}
library(tidyverse)
library(ggplot2)
```

Load Data

```{r}
ccre_table <- data.frame(read_tsv("/Users/christianmei/Documents/Boston_University/Fall_2022_Research/TF_prediction_results/Hypotheses/uncharacterized_crm_hypothesis/cluster_medium_H3K4me1/cluster_regions_filtered.bed", col_names = FALSE))

head(ccre_table)
```

Use coordinates to calculate size

```{r}
ccre_table <- ccre_table %>% mutate(
  size = X3 - X2
)

head(ccre_table)
```

Plot sizes

```{r}
ccre_hist <- ggplot(ccre_table, aes(x = size)) +
  geom_histogram(color = "black", fill = "lightblue") +
  labs(x = "cCRE size (bp)", y = "Frequency") +
  theme_classic()

plot(ccre_hist)
ggsave("ccre_size_hist.pdf", plot = ccre_hist, width = 6, height = 4, units = "in")

```

Take high confidence cCREs and also measure their size. These fragments have covered the entire ATAC-seq peak

```{r}
hcre_table <- data.frame(read_tsv("/Users/christianmei/Documents/Boston_University/Fall_2022_Research/TF_prediction_results/Hypotheses/uncharacterized_crm_hypothesis/candidate_enahncers.bed", col_names = FALSE))

hcre_table <- hcre_table %>% mutate(
  size = X3 - X2
)

hcre_table
```

Get the mean size

```{r}
mean(ccre_table$size)
```

Compare with the initial cluster sizes

```{r}
hcre_old <- ccre_table %>% filter(X4 == "16864" |
                                  X4 == "12859" |
                                    X4 == "3330"|
                                    X4 == "9323" |
                                    X4 == "11869")

hcre_old
```
